%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.4, 27 July 2018) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%
\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}
%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font 
%% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Navy}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%% sample.bib contains your publications
\addbibresource{sample.bib}

\usepackage[colorlinks]{hyperref}

\begin{document}

\name{Timothy Holden}
\tagline{Master of Science in Electrical Engineering Student\\University of Colorado Colorado Springs}
% \photo{2.8cm}{Globe_High}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{th1622ee@gmail.com}
  \phone{+17196668688}
%  \mailaddress{Address, Street, 00000 County}
%  \location{Gwalior, India}
%  \homepage{abhinavj004.github.io}
%  \twitter{@marissamayer}
  \linkedin{https://www.linkedin.com/in/th1622ee/}
  \newline
%   \github{https://github.com/Earth-Worm-Tim} % I'm just making this up though.
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
%   \orcid{orcid.org/0000-0000-0000-0000}
}

%% Make the header extend all the way to the right, if you want. 
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}


%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cvevent{Principal RF Engineer}{Northrop Grumman Corporation}{Jul 2023 -- Present}{Aurora, CO}
\begin{itemize}
\item Designing new and upgrading existing radar-based antennas and ground systems.  
\item Develop models and simulations in support of developmental efforts and analysis of existing systems.
\end{itemize}
%\divider
\medskip
%\smallskip

\cvevent{Software Engineer}{Northrop Grumman Corporation}{Nov 2022 -- Jul 2023}{Aurora, CO}
\begin{itemize}
\item Developed software in Java used to interface with ground terminal hardware in our supervisory level antenna control system.
\item Developed embedded software using Python in support of multiple variants of a multi-band feed for radar-based applications.
\end{itemize}
%\divider
\medskip
%\smallskip

\cvevent{Modeling and Simulation Engineer}{Raytheon Technologies}{May 2022 -- Nov 2022}{Tucson, AZ}
\begin{itemize}
\item Designed high-fidelity models and simulations for RF and EO/IR missile seekers for developmental hypersonic missile defense applications.
\item Developed algorithms in support of the Signal Processing and Guidance, Navigation, and Control Systems.
\end{itemize}
%\divider
\medskip
%\smallskip

\cvevent{RF Test Engineer}{LinQuest Corporation}{Sep 2021 -- May 2022}{Colorado Springs, CO}
\begin{itemize}
\item Performed RF system level integration testing of hardware and software for MILSATCOM ground systems.
\item Performed root-cause-analysis of observed anomalous behavior in MILSATCOM ground terminals and antennas.
\end{itemize}
%\divider
\medskip
%\smallskip

\cvevent{Lead Test Engineer}{United States Space Force}{Sep 2020 -- Sep 2021}{Colorado Springs, CO}
\begin{itemize}
\item Validated test plans and procedures met operational requirements.
\item Supervised all test and evaluation of operational assets in support of US Space Command.
\end{itemize}
%\divider
\medskip
%\smallskip

\cvevent{Associate Engineer}{AMNS Calvert LLC}{Jun 2019 -- Sep 2020}{Calvert, AL}
\begin{itemize}
\item Performed integration of instrumentation in control system network of the Cold Rolling Mill.
\item Developed and implemented programmable logic for new instrumentation.
\end{itemize}
%\divider
%\medskip
\newpage

\cvsection[page2sidebar]{Projects}

\cvevent{Comparative Analysis of Satellite Constellations }{Satellite Communications Semester Project}{08/2022 -- 10/2022}{}
\begin{itemize}
    \item Developed MATLAB simulation of GEO, MEO, and LEO satellites to display ground tracks and footprints.
    \item Used AEHF satellites for GEO, GPS satellites for MEO, and Starlink satellites for LEO tracks.
    \item Created the simulation for the purpose of conducting a comparative analysis of each constellation to study the advantages and disadvantages relative to use cases.
\end{itemize}
\medskip
\divider

\cvevent{Convolutional Encoding and Decoding Simulation}{Satellite Communications Semester Project}{10/2022 -- 12/2022}{}
\begin{itemize}
    \item Developed a simulation of a convolutional encoder and decoder using MATLAB to study the advantages of the encoding and decoding schemes in the presence of noisy channels and a higher bit error rate (BER) probability.
\end{itemize}
\divider
\medskip

\cvevent{Region Specific Image Enhancement of Non-Uniformly Illuminated Images}{Digital Image Processing Semester Project}{08/2020 -- 12/2020}{}
\begin{itemize}
    \item Developed a program to regionally classify areas of excessive illumination causing deterioration of image resolution as opposed to conventional global image processing techniques for enhancement using MATLAB.
    \item The method discovered to yield the greatest result was to convert the image to an HSV image and isolate the intensity layer (V) for regional classification of affected areas using a kernel proportional to obtain image entropy, contrast, and intensity characteristics.
    \item The original image was evaluated using the Rayleigh distribution with clip limits and through adaptive histogram equalization of regions classified as under or over-exposed resulted in a reduction of global standard deviation compared to the original image by approximately 32.4\% globally. 
\end{itemize}
\divider
%\medskip

\cvsection{Research Interests}
\begin{itemize}
    \item Radar-based Antenna Design in PNT Inhibited Environments
    \item Substrate Integrated Waveguide Filter Design
    \item Adaptive Beam Steering for mmWave MU-MIMO Antenna Arrays
    \item Multi-band Phased Array Antennas
    \item Computational Electromagnetics
    \item Space Time Adaptive Processing
    \item Metamaterial-based Adaptive and Reconfigurable Radomes
\end{itemize}

\medskip
% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}


\clearpage




%% If the NEXT page doesn't start with a \cvsection but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the 
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}

\end{document}
